
\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE 
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Yashwant}{Saini}{ \urlstyle{same}\href{http://meyash.xyz}{meyash.xyz } | \href{mailto:yashsn2127@gmail.com}{yashsn2127@gmail.com} | {+91xxxxxxxxxx}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.34\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Thapar Institute of \\ Engineering \& Technology}
%\subsection{Thapar University}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\descript{B.E. in Computer Engineering}
\location{2018 - 2022 | Patiala, Punjab}
\location{CGPA: 8.65/10}
\sectionsep

% \subsection{Aggarsain Public School}
% \descript{Secondary | Senior Secondary}
% \location{Kurukshetra, Haryana}
% \location{10th CBSE 2016 | CGPA: 9.4}
% \location{12th CBSE 2018 | \%age: 90.2}
% \sectionsep 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Portfolio: \href{https://meyash.xyz}{\bf meyash.xyz} \\
Github: \href{https://github.com/meyash}{\bf github.com/meyash} \\
LinkedIn:  \href{https://www.linkedin.com/in/meyash21}{\bf linkedin.com/in/meyash21} \\
Twitter:  \href{https://twitter.com/meyash21}{\bf twitter.com/meyash21}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\location{Languages:} 
C/C++, Python, JavaScript \\
\location{Frameworks:}
Node.js, Django, React.js, Flask \\
\location{Databases:} 
SQL, MongoDB \\
\location{Tools:}
Git, Docker, Linux \\
\location{Familiar:}
Azure, AWS, Android 
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Undergraduate}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
Data Structures and Algorithms \\
Database Management Systems \\
Computer Networking \\
Operating System \\
OOPS \\
Data Science \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     ACHIEVEMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Achievements}
\begin{tabular}{rll}
2021 & 3 STAR | CodeChef \\
2021 & Fellowship | Aarogya Prahari \\
2019 & Winner ELC Hackathon \\
2014 & First AID Second Runner Ups \\
2014 & NCC "A" GRADE Certification\\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    {\footnotesize \textit{\textbf{(Research Asst. \& Teaching Asst 2x) }}} \\
% Unix Tools and Scripting \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.65\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{UBS}
\descript{| SOFTWARE ENGINEER INTERN }
\location{June 2021 – Present | Remote}
\sectionsep

\runsubsection{INNOVATIONM}
\descript{| BACKEND DEVELOPER INTERN }
\location{March 2021 – May 2021 | Remote}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Developed the complete REST API for the internal Asset Management Portal of the company using Node.js, Express.js, and MongoDB.
\item Designed the complete Non-Relational Database schema using MongoDB.
\item Documentation of the API using POSTMAN.
\end{tightemize}
\sectionsep

\runsubsection{AAROGYA PRAHARI}
\descript{| PROJECT FELLOW }
\location{July 2020 – August 2020 | Remote}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Developed a Multilingual Chat Interface for Aarogya Prahari's official website to query all the latest information regarding coronavirus in every state and city.
\item Beautiful soup library was used to fetch live data from government websites and Interface was developed in HTML, CSS, and JavaScript.
\item Chat Interface is live on Aarogya Prahari's official Website.
\end{tightemize}
\sectionsep

%\runsubsection{THAPAR INSTITUTE}
%\descript{| STUDENT DEVELOPER }
%\location{August 2020 – September 2020 | Remote}
%\begin{tightemize}
%\item Developed chat User Interface using HTML, CSS, JS.
%\item Deployed the Flask Backend on Azure VM.
%\item Deployed frontend as CDN on npm.
%\end{tightemize}
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection{THAPAR CHATBOT}
% \descript{}
\location{}
\begin{tightemize}
\item Developed an Intent and Flow-based Hybrid chatbot for Thapar University’s Homepage to help parents and students with the admission process.
\item Supported training in multiple languages.
\item The Chatbot was live on Thapar's official website for 6 months.
\end{tightemize}
\sectionsep

\runsubsection{MAJESTIC PDF ANALYSIS PORTAL} \href{https://github.com/meyash/majestic}{\bf Github}
\location{}
\begin{tightemize}
\item Majestic is a complete PDF searching, analysis, and summarisation portal for PHD students.
\item Features - Authentication, WordClouds, Summarization, Context Searching, Chatting & Scraping Assistants.
\item Currently in Testing Phase.
\end{tightemize}
\sectionsep

\runsubsection{DOCKER PRODUCTION WORKFLOW} \href{https://github.com/meyash/docker_production_workflow}{\bf  Github}
\location{}
\begin{tightemize}
\item Developed Docker Workflow for Testing and Production in React.
\item Used Docker Compose, NGINX Webserver, Docker Volumes Setup.
\item Testing was set up using Travis CI.
\item Deployment on AWS Elastic Beanstalk.
\end{tightemize}
\sectionsep

%\runsubsection{JUPYTERLAB WEATHER EXTENSION} \href{https://github.com/meyash/jupyterlab_weather_extension}{\bf Github}
%\location{}
%\begin{tightemize}
%\item A weather query extension for JupyterLab.
%\item Tech Stack – React.js, JavaScript, Python.
%\item Deployed on npm.
%\end{tightemize}
%\sectionsep

\runsubsection{WOLWO UI} \href{https://github.com/meyash/wolwo}{\bf Github}
\location{}
\begin{tightemize}
\item User Interface for an OpenSource Wallpaper application.
\item Developed in Dart and Flutter.
\item WOLWO has a Homepage, Collections page, Wallpaper-View page, and Settings page showing information about the device.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Awards} 
% \begin{tabular}{rll}
% 2014	     & top 52/2500  & KPCB Engineering Fellow\\
% 2014	     & 1\textsuperscript{st}/50  & Microsoft Coding Competition, Cornell\\
% 2013	     & National  & Jump Trading Challenge Finalist\\
% 2013     & 7\textsuperscript{th}/120 & CS 3410 Cache Race Bot Tournament  \\
% 2012     & 2\textsuperscript{nd}/150 & CS 3110 Biannual Intra-Class Bot Tournament \\
% 2011     & National & Indian National Mathematics Olympiad (INMO) Finalist \\
% \end{tabular}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Publications} 
% \renewcommand\refname{\vskip -1.5em} % Couldn't get this working from the .cls file
% \bibliographystyle{abbrv}
% \bibliography{publications}
% \nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}
